Type Visualization for R

### 2020-06-18 paper/main.tex
paper: Add technical details section

These different components support different modes of search.
If a user has a specific function in mind,
the search bar supports fuzzy autocomplete
that can quickly select a function among thousands.
However, if one wants to browse
all available functions and packages,
the treemap view is more applicable.
Nodes in the bottom treemap convey the log-scaled
frequency of function calls,
and correspondingly the top treemap
is scaled based on invocations
of functions defined in that package.
Log-scaling and pagination keep
elements of the treemap legible,
even if absolute size differences are significant.

@@

% d3, vue

% backend node, sqlite3, indexing

@@

\todo{Should say this is not R specific. Point limitations.}

@@

>>>>

These different components support different modes of search.
If a user has a specific function in mind,
the search bar supports autocomplete
that can quickly select a function among thousands.
However, if one wants to browse
all available functions and packages,
the treemap view is more applicable.
Nodes in the bottom treemap convey the log-scaled
frequency of function calls,
and correspondingly the top treemap
is scaled based on invocations
of functions defined in that package.
Log-scaling and pagination keep
elements of the treemap legible,
even if absolute size differences are significant.

@@

Since the amount of data that a user may query is large,
the application consists of both a frontend and a backend.

On the frontend, state management, interactivity,
and DOM manipulation is all done within the Vue framework.
This is in contrast with many web-based visualizations
that use D3 for DOM manipulation.
We chose this setup because of the many different
individual components whose state must be kept
sychronized.
This includes not only the visualizations, but also
user interface elements like the autocomplete search bar.
In our experience, Vue's model of reactivity is
more successful at maintaining consistency across the
entire system than using D3 and vanilla JavaScript.
While {\sc TypeVis} does not use D3 for DOM manipulation,
it still does use D3 for other visualization-related
computations.

Our backend is a Node.js application that serves
JSON in a standard REST-style architecture.
Data is stored in a SQLite database that has been
indexed to achieve lookups as fast as possible.

@@

\todo{Point limitations.}

@@

% more type system features (dimensionality, dispatch)
% other languages
% general philosophy, not just about types
